Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-03-10 area_agg_seq_tsas.tex
added the proof of NP-hardness

\begin{document}
\title{Finding Optimal Sequences for Area Aggregation  
	---\protect\\ 
	\Astar vs. Integer Linear Programming}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

Maps are the main tool to represent geographical information. 
As geographical information is usually scale-dependent
\parencite{Muller1995Generalization,Weibel1997}, 
users need to have access to maps at different scales.
In order to generate these maps,
national mapping agencies produce a base map
and then derive maps at smaller scales by 
\emph{map generalization}
More specifically, 
map generalization is the process of extracting and arranging
geographical information from detailed data in order to produce maps
at smaller scales.
A requirement of map generalization is to emphasize the 
essential while suppress the unimportant,
and at the same time maintain logical relationship between 
objects \parencite{Weibel1997}.
As manual generalization is labor-intensive
\parencite{Duchene2014},
automating map generalization is a promising way 
to produce up-to-date maps at high speed and low cost 
\parencite{Mackaness2017Generalization}.

@@

In this chapter, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map. 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
Then, we compare three methods for finding aggregation sequences.
First, we develop 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we present a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and then we solve this program with minimizing our cost function.
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

We do not deal with simplifying polylines in this chapter.
The simplification can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973},
\textcite{Saalfeld1999},
or \textcite{Wu2004DP}.
Those methods can be used to set up 
the binary line generalisation tree (BLG-tree) of
\textcite{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.
%
Although splitting polygons is a good step
of generalizing land-cover areas,
we do not integrate it into our method at this moment.
Some examples of splitting are as follows.
\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
proposed to split tiny polygons 
and then to merge the split parts into the neighboring polygons.
\textcite{Meijers2016Split} developed an algorithm 
to split a polygon (the splittee) 
based on a constrained Delaunay triangulation.
During splitting, their algorithm is capable of
taking into account
the attractivenesses between the splittee and its neighbors.
When merging, a more attractive neighbor 
will get a larger portion from the splittee.

@@

\mypar{Model}
We consider a directed graph $G$, 
which we call the \emph{subdivision graph} 
(see \fig\ref{fig:AreaAgg_SubdivisionName}). 
The node set $V$ of~$G$ contains a node for every
possible map (or \emph{subdivision}), including the start map, all
possible intermediate-scale maps, and the goal map.
The arc set~$E$ of~$G$ contains an arc $(\Pnode, P_{t+1,j})$ 
between any two maps~$\Pnode$ and~$P_{t+1,j}$ in~$V$ 
if~$P_{t+1,j}$ can be reached from~$\Pnode$ 
with a single aggregation operation,
involving a smallest area.
Then, any directed path in~$G$ from the start map to the goal map
defines a possible aggregation sequence.
Our idea is to obtain an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal.
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G$ can be huge as we will argue later.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that we only know 
subdivisions~$\Pstart$ and~$\Pgoal$ at the beginning.
We generate a subdivision (node) only when we want to visit it.

\begin{figure}[tb]
\centering
\includegraphics[page=3]{AreaAgg_Preliminaries}
\caption{The subdivision graph~$G$. 
	The nodes of the graph are the subdivisions. 
	There is an arc	from subdivision~\Pnode 
	to subdivision~${P}_{t+1,j}$ 
	if~${P}_{t+1,j}$ is the result of 
	an aggregating step from~\Pnode.}
\label{fig:AreaAgg_SubdivisionName}
\end{figure}

@@

\mypar{Exponential lower bound}
We now analyze the size of subdivision graph~$G$.
Our analysis is inspired by \textcite{Keane1975Size},
where we also use a row of~$n$~areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangles,
and the goal map is simply the union of the~$n$ rectangles.
At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
intermediate vertical boundaries. 
For this, the number of choices is~$
\binom{2k}{k}
= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
{k\cdot (k-1)\cdot \ldots \cdot 1}
\ge 2^k = 2^{(n-1)/2}$.
That is to say, the size of our model
has an exponential lower bound.

@@

Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$. 
In this step, patch~$u$ is aggregated into patch~$v$
(see \figs\ref{fig:AreaAgg_FirstStep}a 
and \ref{fig:AreaAgg_FirstStep}b).
We denote the types of the two patches by~$T(u)$ and~$T(v)$. 
We define the cost of type change of this step by
\begin{equation}
\label{eq:f_type}
f_\mathrm{type}(P_{s,i},P_{s+1,j})=\frac{A_{u}}{A_R}
\cdot
\frac{d(T(u),T(v))}{T_{\max}},
\end{equation}
where~$A_u$ is the area of patch~$u$, 
and~$A_R$ is the area of region~$R$
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We use~$A_R$ and~$T_{\max}$ 
to normalize the cost of type change. 
Constant~$T_{\max}$, the maximum cost over all type changes,  
is known from the input. 
The input specifies, for each pair~$(T_1,T_2)$ of types, 
cost~$d(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
Specifically, we denote by~$T_\mathrm{goal}$ the type of 
the patch on the goal map.
For simplicity, we use a metric 
as the cost function of type change
(see \sect\ref{sec:AreaAgg_CaseStudy}); 
\textcite[\chap2]{Choudhary1992Elements}
shows the definition of a metric.
A metric distance is symmetric, 
which is different from the non-symmetric one used in
\textcite{Dilo2009tGAP}.
In their definition, for example, 
the distance from type \emph{building} to type \emph{road} is~$0.5$,
but the distance from \emph{road} to \emph{building} is~$0$.

@@

\sect\ref{sec:AreaAgg_Preliminaries} has shown that
the size of finding an optimal aggregation sequence 
can be exponential.
That is to say, the graph~$G$---our search space---can 
be of exponential size.
In order to avoid computing the whole graph explicitly,
we use the \Astar algorithm \parencite{Hart1968,PatelAStar}.
To save time and memory, 
we generate a subdivision, \Pnode, only 
when we are going to visit it.
\Astar uses a clever best-first search 
to find a shortest path 
from subdivision~$\Pstart$ to subdivision~$\Pgoal$.  
For \Pnode,
\Astar considers the exact cost of a shortest path 
from~\Pstart to~\Pnode 
and estimates the cost to get from~\Pnode to~\Pgoal. 
\Astar explores the nodes earlier 
if they are estimated to be closer to the goal.
\Astar can be seen as a refinement of Dijkstra's algorithm
\parencite{Dijkstra1959}.

@@

To narrow down the search space, 
we set up estimation functions 
for type change (\sect\ref{sec:AreaAgg_h_type}), 
compactness (\sect\ref{sec:AreaAgg_h_comp}), 
and length (\sect\ref{sec:AreaAgg_h_length}). 
These functions are meant to direct \Astar towards the goal.
Since the number of subdivisions can be exponential, 
we may run out of the main memory 
before we find an optimal solution. 
To handle this problem, we introduce overestimations 
to find a feasible solution. 
Overestimations are popular 
when people cannot find optimal solutions using \Astar. 
For example, \textcite{Pohl1973} overestimated 
using dynamic weighting. 
We propose another strategy that fits our problem. 
We first try finding an optimal solution by \Astar. 
If we fail to find one after 
we have visited a predefined number, 
say,~$W$ of nodes of graph~$G$,
then we restart.
In the retrying, we overestimate the first~$K$ steps 
starting at each node
(see \sects\ref{sec:AreaAgg_h_type}, \ref{sec:AreaAgg_h_comp},
and~\ref{sec:AreaAgg_h_length}).
We may need to increase~$K$ and retry several times 
until we find a feasible solution.
Because we do not want to retry too many times,
we define~$K$ by
\begin{equation}
\label{eq:OverestimateK}
K= 2^k -1,
\end{equation}
where~$k\ge 0$ is the number of retryings.
When~$k = 0$, we have~$K=0$,
which means that the first attempt of finding a solution
does not use overestimation.
As~$K\le n-1$, it holds that~$k \le \log_2 n$, 
which means that we need to 
retry~$\lceil \log_2 n\rceil$ times at most.
Whenever overestimating ($k\geq1$), 
\Astar cannot guarantee optimality anymore.
When we are at time~$t$, there are at most~$n-t$ steps 
to arrive at the goal map.
We define the number of practical overestimation steps as
\begin{equation}
\label{eq:OverestimateKPrime}
K'= \min \{K, n-t\}.
\end{equation}

@@

We tested our method on a dataset 
from the German topographic database ATKIS DLM~50. 
The dataset represents the place 
``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
Our start map is the result of collapsing areas 
by \citet[\chap6]{haunert2008f}.
The start map has~$5{,}537$ polygons. 
Our goal map was generalized from the start map 
by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
The goal map has~$734$ polygons, 
which means that there are~$N=734$ regions.
The distribution of region sizes is shown in 
\fig\ref{fig:AreaAgg_NumRegion}.
%
We used a tree-based method introduced by 
\citet{Rada1989SemanticMetric} 
to define the distances of the types;
the distance is the ``number of edges'' that
we need to travel from one node to another node in the tree of 
type hierarchy\footnote{More information 
    about land-cover types can be found at 
	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
	Accessed: Nov 1, 2017.}
(see \fig\ref{fig:AreaAgg_TypeDistances}). 
For example, the distance from type \emph{village}
to type \emph{fence} is~$2$, 
to type \emph{street} is~$4$, and
to type \emph{farm land} is~$6$.
In this tree, the maximum distance is~$6$, 
which means~$T_\mathrm{max}=6$ for \eq\ref{eq:f_type}.
According to \citet{Rada1989SemanticMetric}, 
the resulting cost function for type change is a metric.

@@

As illustrated in \sect\ref{sec:AreaAgg_Combining},
we compare \Astar and the greedy algorithm using $g_1(\Pnode)$,
which is a combination of the costs 
of type change and compactness (see \eq\ref{eq:g_1}).
For \Astar, we overestimated 
whenever we could not find a solution after 
having visited~$W$ nodes 
(see \sect\ref{sec:AreaAgg_AStar}).
We tried~$W=200{,}000$ and~$W=400{,}000$
(if we could use more main memory, 
then we could test by using some larger~$W$). 
The results are shown in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
%
Comparing to \Astar, 
the greedy algorithm visited 
fewer nodes and arcs in graph~$G$ 
and used much less time.
However, \Astar managed to find solutions with 
lower total cost,~$117.3$ (or~$117.2$), 
which is~$2.8\%$ less than 
the total cost of the greedy algorithm,~$120.7$.
%
When~$W=200{,}000$, we are sure that 
we have found optimal solutions 
for~$702$ of the~$734$ regions ($95.6\%$),
while the greedy algorithm solved 
only~$408$ ($55.6\%$) to optimality;
see column \#OS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
For the other~$32$ regions, 
both algorithms have found feasible solutions 
(see column \#FS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
Although some of the feasible solutions may also be optimal,
we cannot verify that only from the cost values.

>>>>

\fancyhead[LO]{Finding Optimal Sequences for Area Aggregation}

\begin{document}
\title{Finding Optimal Sequences for Area Aggregation---\protect\\ 
	\Astar vs. Integer Linear Programming
    }
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

Maps are the main tool to represent geographical information. 
As geographical information is usually scale-dependent
\parencite{Muller1995Generalization,Weibel1997}, 
users need to have access to maps at different scales.
In order to generate these maps,
national mapping agencies produce a base map
and then derive maps at smaller scales by 
\emph{map generalization}.
More specifically, 
map generalization is the process of extracting and arranging
geographical information from detailed data in order to produce maps
at smaller scales.
A requirement of map generalization is to emphasize the 
essential while suppress the unimportant,
and at the same time maintain logical relationship between 
objects \parencite{Weibel1997}.
As manual generalization is labor-intensive
\parencite{Duchene2014},
automating map generalization is a promising way 
to produce up-to-date maps at high speed and low cost 
\parencite{Mackaness2017Generalization}.

@@

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map. 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(\sect\ref{sec:AreaAgg_Preliminaries}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
Then, we compare three methods for finding aggregation sequences.
First, we develop 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we present a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and then we solve this program with minimizing our cost function.
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

We do not deal with simplifying polylines in this paper.
The simplification can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973},
\textcite{Saalfeld1999},
or \textcite{Wu2004DP}.
Those methods can be used to set up 
the binary line generalisation tree (BLG-tree) of
\textcite{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.
%
Although splitting polygons is a good step
of generalizing land-cover areas,
we do not integrate it into our method at this moment.
Some examples of splitting are as follows.
\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
proposed to split tiny polygons 
and then to merge the split parts into the neighboring polygons.
\textcite{Meijers2016Split} developed an algorithm 
to split a polygon (the splittee) 
based on a constrained Delaunay triangulation.
During splitting, their algorithm is capable of
taking into account
the attractivenesses between the splittee and its neighbors.
When merging, a more attractive neighbor 
will get a larger portion from the splittee.

@@

\mypar{Model}
We consider a directed graph $G_\mathrm{S}$, 
which we call the \emph{subdivision graph} 
(see \fig\ref{fig:AreaAgg_SubdivisionName}). 
The node set $V_\mathrm{S}$ of~$G_\mathrm{S}$ 
contains a node for every
possible map (or \emph{subdivision}), including the start map, 
all possible intermediate-scale maps, and the goal map.
The arc set~$E_\mathrm{S}$ of~$G_\mathrm{S}$ 
contains an arc $(\Pnode, P_{t+1,j})$ 
between any two maps~$\Pnode$ and~$P_{t+1,j}$ in~$V_\mathrm{S}$ 
if~$P_{t+1,j}$ can be reached from~$\Pnode$ 
with a single aggregation operation,
involving a smallest area.
Then, any directed path in~$G_\mathrm{S}$ 
from the start map to the goal map
defines a possible aggregation sequence.
Our idea is to obtain an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal.
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G_\mathrm{S}$ can be huge as we will argue later.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that we only know 
subdivisions~$\Pstart$ and~$\Pgoal$ at the beginning.
We generate a subdivision (node) only when we want to visit it.

\begin{figure}[tb]
\centering
\includegraphics[page=3]{AreaAgg_Preliminaries}
\caption{The subdivision graph~$G_\mathrm{S}$. 
	The nodes of the graph are the subdivisions. 
	There is an arc	from subdivision~\Pnode 
	to subdivision~${P}_{t+1,j}$ 
	if~${P}_{t+1,j}$ is the result of 
	an aggregating step from~\Pnode.}
\label{fig:AreaAgg_SubdivisionName}
\end{figure}

@@

Sometimes, we need a graph to represent the adjacencies of
the land-cover areas in a subdivision,
we call such a graph $G_\mathrm{A}$
(see \fig\ref{fig:AreaAgg_Variables_Graph}).

\mypar{Exponential lower bound}
We now analyze the size of subdivision graph~$G_\mathrm{S}$.
Our analysis is inspired by \textcite{Keane1975Size},
where we also use a row of~$n$~areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangles,
and the goal map is simply the union of the~$n$ rectangles.
At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
intermediate vertical boundaries. 
For this, the number of choices is~$
\binom{2k}{k}
= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
{k\cdot (k-1)\cdot \ldots \cdot 1}
\ge 2^k = 2^{(n-1)/2}$.
That is to say, the size of our model
has an exponential lower bound.

\section{NP-hardness Proof}
\label{sec:AreaAgg_NP-hardness}

Although we have shown that the graph of subdivisions
has an exponential size,
one may develop a clever algorithm 
to find an optimal sequence efficiently.
In the following, we prove that 
finding such a sequence is indeed NP-hard.
In the proof, we neglect the cost of compactness or the cost of length.
Considering one of the two costs 
will make the finding even more difficult.

\newtheorem{thm}{Theorem}
\begin{thm}
\textsc{AreaAggregationSequence} is NP-hard 
even if we only consider the cost of type change.
\end{thm}

\begin{proof}
Our NP-hardness proof is by reduction from 
the NP-complete problem \textsc{PlanarVertexCover}, 
which is to decide, for a given 
planar graph~$G_\mathrm{A} = (V_\mathrm{A},E_\mathrm{A})$, 
whether there exists a vertex cover 
with at most a given number~$k_\mathrm{A}$ of vertices. 
For an instance of \textsc{PlanarVertexCover}
(\fig\ref{fig:AreaAgg_Reduction}a), 
we define a corresponding instance of \textsc{AreaAggregationSequence}
whose start map consists of red, black, and white areas and 
whose goal map consists of only one large red patch.
The adjacency graphs of the two maps are illustrated 
in \figs\ref{fig:AreaAgg_Reduction}b and~\ref{fig:AreaAgg_Reduction}c, 
where the colors of the vertices represent 
the colors of the corresponding areas.
More precisely, for each vertex of~$G_\mathrm{A}$
in \fig\ref{fig:AreaAgg_Reduction}a, 
we define a red vertex and a black vertex, 
which we connect with an edge. 
For each edge of~$G_\mathrm{A}$, 
we define two white vertices and 
connect them with the two black vertices
(\fig\ref{fig:AreaAgg_Reduction}b).

\begin{figure}[h]
\centering
\includegraphics[page=1]{AreaAgg_NPHard}
\caption{The reduction for our NP-hardness proof.
    The dashed polygon in (c) shows 
    that the vertices are merged.}
\label{fig:AreaAgg_Reduction}
\end{figure}

We define the weights of the vertices 
in \fig\ref{fig:AreaAgg_Reduction}b as follows:
\begin{itemize}
\item Every white vertex has weight~$1$.
\item Every black vertex has weight~$2$.
\item Every red vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
which is equal to the total weight of all white and black vertices.
\end{itemize}
Since in each aggregation step, 
we require the smallest area to be aggregated with one of its neighbors, 
our definition of the weights to a certain degree determines 
the order in which the vertices are selected:
\begin{itemize}
\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
a white vertex is selected and merged with one of its neighbors, 
such that the white vertex receives the neighbor's color or vice versa.
\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
a non-red vertex is selected and merged with one of its neighbors.
\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
\end{itemize}

To complete the reduction, 
we need to define the costs of color changes. 
For any color change, 
we charge one unit of cost per unit weight.
Due to our construction, Phases II and III can be accomplished with
a total cost of~$2|V_\mathrm{A}|+2|E_\mathrm{A}|$, 
no matter how Phase I is accomplished.
This is because, after Phase I, 
every non-red patch will be adjacent to a red patch (vertex).
Thus, if any non-red patch becomes selected in Phase II, 
it can aggregate with a red patch (vertex) and 
receive the color red. 
This implies that Phase II costs $2|V_\mathrm{A}|+2|E_\mathrm{A}|$ 
(which is equal to the total weight of 
all initially white and black vertices) and, 
since after Phase II all patches are red, 
Phase III does not cause any additional cost.  
It is also clear that 
there is no cheaper way to accomplish Phases II and III,
since it is impossible to color a vertex red in Phase I.
Consequently, since the total cost of Phases II and III is fixed, 
it is only interesting to ask 
at which cost Phase I can be accomplished.
It turns out that, if $G_\mathrm{A}$ 
has a vertex cover $C_\mathrm{A} \subseteq V_\mathrm{A}$, 
then Phase I can be accomplished with cost $2|C_\mathrm{A}|$;
only the black vertices corresponding to vertices in~$C_\mathrm{A}$ 
need to change their color from black to white, and 
each of them has weight~$2$ (see \fig\ref{fig:reduction2}).
To summarize, if graph~$G_\mathrm{A}$ has a vertex cover~$C_\mathrm{A}$, 
then the corresponding instance of \textsc{AreaAggregationSequence} 
has a solution of 
total cost~$2|C_\mathrm{A}|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.

It remains to be shown that, 
if $C_\mathrm{A}^*$ is a minimum vertex cover of $G_\mathrm{A}$, 
then there is no solution with total cost 
less than $2|C_\mathrm{A}^*|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.
To see why, we assume that such a solution exists.
If we keep the black color of a vertex from $C_\mathrm{A}^*$ 
(the total cost decreases by $2$),
then we will need to at least change two white vertices
to black vertices
(the total cost increases by $2$ at least).
Therefore, we have found a contradiction to our assumption.

\begin{figure}[h]
\centering
\includegraphics[page=2]{AreaAgg_NPHard}
\caption{The situation after Phase I has been conducted 
    such that all black vertices corresponding to a vertex cover 
    of~$G_\mathrm{A}$ have been recolored white.
    The dashed polygons show that the vertices are merged.}
\label{fig:reduction2}
\end{figure}
\end{proof}

@@

Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$. 
In this step, patch~$u$ is aggregated into patch~$v$
(see \figs\ref{fig:AreaAgg_FirstStep}a 
and \ref{fig:AreaAgg_FirstStep}b).
We denote the types of the two patches by~$T(u)$ and~$T(v)$. 
We define the cost of type change of this step by
\begin{equation}
\label{eq:f_type}
f_\mathrm{type}(P_{s,i},P_{s+1,j})=\frac{A_{u}}{A_R}
\cdot
\frac{d(T(u),T(v))}{T_{\max}},
\end{equation}
where~$A_u$ is the area of patch~$u$, 
and~$A_R$ is the area of region~$R$
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We use~$A_R$ and~$T_{\max}$ 
to normalize the cost of type change. 
Constant~$T_{\max}$, the maximum cost over all type changes,  
is known from the input. 
The input specifies, for each pair~$(T_1,T_2)$ of types, 
cost~$d(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
Specifically, we denote by~$T_\mathrm{goal}$ the type of 
the patch on the goal map.
For simplicity, we use a metric 
as the cost function of type change
(see \sect\ref{sec:AreaAgg_CaseStudy}); 
\textcite[\chap2]{Choudhary1992Elements}
shows the definition of a metric.
A metric distance is symmetric, 
which is different from the asymmetric one used in
\textcite{Dilo2009tGAP}.
In their definition, for example, 
the distance from type \emph{building} to type \emph{road} is~$0.5$,
but the distance from \emph{road} to \emph{building} is~$0$.

@@

\sect\ref{sec:AreaAgg_Preliminaries} has shown that
the size of finding an optimal aggregation sequence 
can be exponential.
That is to say, the graph~$G_\mathrm{S}$---our search space---can 
be of exponential size.
In order to avoid computing the whole graph explicitly,
we use the \Astar algorithm \parencite{Hart1968,PatelAStar}.
To save time and memory, 
we generate a subdivision, \Pnode, only 
when we are going to visit it.
\Astar uses a clever best-first search 
to find a shortest path 
from subdivision~$\Pstart$ to subdivision~$\Pgoal$.  
For \Pnode,
\Astar considers the exact cost of a shortest path 
from~\Pstart to~\Pnode 
and estimates the cost to get from~\Pnode to~\Pgoal. 
\Astar explores the nodes earlier 
if they are estimated to be closer to the goal.
\Astar can be seen as a refinement of Dijkstra's algorithm
\parencite{Dijkstra1959}.

@@

To narrow down the search space, 
we set up estimation functions 
for type change (\sect\ref{sec:AreaAgg_h_type}), 
compactness (\sect\ref{sec:AreaAgg_h_comp}), 
and length (\sect\ref{sec:AreaAgg_h_length}). 
These functions are meant to direct \Astar towards the goal.
Since the number of subdivisions can be exponential, 
we may run out of the main memory 
before we find an optimal solution. 
To handle this problem, we introduce overestimations 
to find a feasible solution. 
Overestimations are popular 
when people cannot find optimal solutions using \Astar. 
For example, \textcite{Pohl1973} overestimated 
using dynamic weighting. 
We propose another strategy that fits our problem. 
We first try finding an optimal solution by \Astar. 
If we fail to find one after 
we have visited a predefined number, 
say,~$W$ of nodes of graph~$G_\mathrm{S}$,
then we restart.
In the retrying, we overestimate the first~$K$ steps 
starting at each node
(see \sects\ref{sec:AreaAgg_h_type}, \ref{sec:AreaAgg_h_comp},
and~\ref{sec:AreaAgg_h_length}).
We may need to increase~$K$ and retry several times 
until we find a feasible solution.
Because we do not want to retry too many times,
we define~$K$ by
\begin{equation}
\label{eq:OverestimateK}
K= 2^k -1,
\end{equation}
where~$k\ge 0$ is the number of retryings.
When~$k = 0$, we have~$K=0$,
which means that the first attempt of finding a solution
does not use overestimation.
As~$K\le n-1$, it holds that~$k \le \log_2 n$, 
which means that we need to 
retry~$\lceil \log_2 n\rceil$ times at most.
Whenever overestimating ($k\geq1$), 
\Astar cannot guarantee optimality anymore.
When we are at time~$t$, there are at most~$n-t$ steps 
to arrive at the goal map.
We define the number of practical overestimation steps as
\begin{equation}
\label{eq:OverestimateKPrime}
K'= \min \{K, n-t\}.
\end{equation}

@@

We tested our method on a dataset 
from the German topographic database ATKIS DLM~50. 
The dataset represents the place 
``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
Our start map is the result of collapsing areas 
by \citet[\chap6]{haunert2008f}.
The start map has~$5{,}537$ polygons. 
Our goal map was generalized from the start map 
by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
The goal map has~$734$ polygons, 
which means that there are~$N=734$ regions.
The distribution of region sizes is shown in 
\fig\ref{fig:AreaAgg_NumRegion}.
%
We used a tree-based method introduced by 
\citet{Rada1989SemanticMetric} 
to define the distances of the types;
the distance is the ``number of edges'' that
we need to travel from one node to another node in the tree of 
type hierarchy\footnote{More information 
    about land-cover types can be found at 
%	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
	Accessed: Nov 1, 2017.}
(see \fig\ref{fig:AreaAgg_TypeDistances}). 
For example, the distance from type \emph{village}
to type \emph{fence} is~$2$, 
to type \emph{street} is~$4$, and
to type \emph{farm land} is~$6$.
In this tree, the maximum distance is~$6$, 
which means~$T_\mathrm{max}=6$ for \eq\ref{eq:f_type}.
According to \citet{Rada1989SemanticMetric}, 
the resulting cost function for type change is a metric.

@@

As illustrated in \sect\ref{sec:AreaAgg_Combining},
we compare \Astar and the greedy algorithm using $g_1(\Pnode)$,
which is a combination of the costs 
of type change and compactness (see \eq\ref{eq:g_1}).
For \Astar, we overestimated 
whenever we could not find a solution after 
having visited~$W$ nodes 
(see \sect\ref{sec:AreaAgg_AStar}).
We tried~$W=200{,}000$ and~$W=400{,}000$
(if we could use more main memory, 
then we could test by using some larger~$W$). 
The results are shown in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
%
Comparing to \Astar, 
the greedy algorithm visited 
fewer nodes and arcs in graph~$G_\mathrm{S}$ 
and used much less time.
However, \Astar managed to find solutions with 
lower total cost,~$117.3$ (or~$117.2$), 
which is~$2.8\%$ less than 
the total cost of the greedy algorithm,~$120.7$.
%
When~$W=200{,}000$, we are sure that 
we have found optimal solutions 
for~$702$ of the~$734$ regions ($95.6\%$),
while the greedy algorithm solved 
only~$408$ ($55.6\%$) to optimality;
see column \#OS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
For the other~$32$ regions, 
both algorithms have found feasible solutions 
(see column \#FS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
Although some of the feasible solutions may also be optimal,
we cannot verify that only from the cost values.
